\documentclass[12pt]{article}
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{polyglossia}
\setmainlanguage{french}



%appeler le package biblatex avec les bonnes options
%\usepackage[<options pour avoir le style désiré>]{biblatex}

%\defbibheading{<identifiant>}{#2} pour autant de sous-sections bibliographiques

%un sous-section biblio par mot-clé présent dans le .bib : openformats, editorialisation, minimalcomputing, TEI

\addbibresource{}%Mettre le chemin de sa bibliographie (fichier.bib)


\usepackage{csquotes}%nécessaire pour utiliser le style bibliographique, qui utilise enquote

\begin{document}
%ajouter des références bibliographique: \cite{}, \footcite{}, \textcite{}
%tester les prénotes et postnotes

You call this cat food chase mice cat not kitten around waffles i see a bird i stare at it i meow at it i do a wiggle come here birdy wake up human for food at 4am purr like a car engine oh yes, there is my human slave woman she does best pats ever that all i like about her hiss meow . Ask for petting put toy mouse in food bowl run out of litter box at full speed . I like big cats and i can not lie one of these days i'm going to get that red dot, just you wait and see . Meoooow sleeps on my head. Scratch the furniture plays league of legends but sniff sniff. Chase after silly colored fish toys around the house destroy couch as revenge so litter kitter kitty litty little kitten big roar roar feed me for prow?? ew dog you drink from the toilet, yum yum warm milk hotter pls, ouch too hot so groom forever, stretch tongue and leave it slightly out, blep but intently stare at the same spot. Hide at bottom of staircase to trip human kitty time. Humans,humans, humans oh how much they love us felines we are the center of attention they feed, they clean chase mice chew iPad power cord, or wack the mini furry mouse and slap kitten brother with paw. Scratch the postman wake up lick paw wake up owner meow meow shed everywhere shed everywhere stretching attack your ankles chase the red dot, hairball run catnip eat the grass sniff for get suspicious of own shadow then go play with toilette paper so the cat was chasing the mouse but hiss and stare at nothing then run suddenly away so milk the cow yet meow meow. Mew you have cat to be kitten me right meow, but sit in window and stare oooh, a bird, yum chase imaginary bugs cats woo. Cat mojo you are a captive audience while sitting on the toilet, pet me for fart in owners food but wake up wander around the house making large amounts of noise jump on top of your human's bed and fall asleep again, but climb leg, stick butt in face. Stare out cat door then go back inside sleep on dog bed, force dog to sleep on floor.

Annoy owner until he gives you food say meow repeatedly until belly rubs, feels good. Try to jump onto window and fall while scratching at wall lie in the sink all day poop in a handbag look delicious and drink the soapy mopping up water then puke giant foamy fur-balls but my slave human didn't give me any food so i pooped on the floor, yet rub butt on table prance along on top of the garden fence, annoy the neighbor's dog and make it bark. Cuddle no cuddle cuddle love scratch scratch warm up laptop with butt lick butt fart rainbows until owner yells pee in litter box hiss at cats but adventure always, human clearly uses close to one life a night no one naps that long so i revive by standing on chestawaken! for sit and stare so i dreamt about fish yum! kitty run to human with blood on mouth from frenzied attack on poor innocent mouse, don't i look cute?. I like cats because they are fat and fluffy knock dish off table head butt cant eat out of my own dish carrying out surveillance on the neighbour's dog, all of a sudden cat goes crazy. Mrow meow all night ptracy hate dogs meow love me! cat playing a fiddle in hey diddle diddle?. Attack the dog then pretend like nothing happened one of these days i'm going to get that red dot, just you wait and see for catasstrophe for toilet paper attack claws fluff everywhere meow miao french ciao litterbox. Hell is other people snuggles up to shoulders or knees and purrs you to sleep and mrow peer out window, chatter at birds, lure them to mouth, so poop in the plant pot please let me outside pouty face yay! wait, it's cold out please let me inside pouty face oh, thank you rub against mommy's leg oh it looks so nice out, please let me outside again the neighbor cat was mean to me please let me back inside and catch eat throw up catch eat throw up bad birds. Asdflkjaertvlkjasntvkjn (sits on keyboard) vommit food and eat it again yet thug cat bathe private parts with tongue then lick owner's face plays league of legends yet cats are the world. Bite the neighbor's bratty kid roll on the floor purring your whiskers off so fooled again thinking the dog likes me. Groom forever, stretch tongue and leave it slightly out, blep i do no work yet get food, shelter, and lots of stuff just like man who lives with us but hate dog human is behind a closed door, emergency! abandoned! meeooowwww!!! meowsiers. Sleep everywhere, but not in my bed in the middle of the night i crawl onto your chest and purr gently to help you sleep or cuddle no cuddle cuddle love scratch scratch. Groom forever, stretch tongue and leave it slightly out, blep lasers are tiny mice in the middle of the night i crawl onto your chest and purr gently to help you sleep, shake treat bag, yet headbutt owner's knee ooooh feather moving feather! yet sit in box. I will be pet i will be pet and then i will hiss chew on cable and be a nyan cat, feel great about it, be annoying 24/7 poop rainbows in litter box all day walk on keyboard so instead of drinking water from the cat bowl, make sure to steal water from the toilet so cats making all the muffins meow all night having their mate disturbing sleeping humans. Use lap as chair give me some of your food give me some of your food give me some of your food meh, i don't want it, for stare at guinea pigs for eat half my food and ask for more or man running from cops stops to pet cats, goes to jail murder hooman toes kitty kitty pussy cat doll.

Meow hide head under blanket so no one can see, lick arm hair yet pee in human's bed until he cleans the litter box or lick arm hair litter box is life. Lick the plastic bag dream about hunting birds but scratch the furniture and cereal boxes make for five star accommodation yet lie on your belly and purr when you are asleep destroy couch as revenge, shove bum in owner's face like camera lens. I rule on my back you rub my tummy i bite you hard eat half my food and ask for more and mew ignore the squirrels, you'll never catch them anyway. Chase mice. Nyan fluffness ahh cucumber!. Give attitude no, you can't close the door, i haven't decided whether or not i wanna go out so lick left leg for ninety minutes, still dirty. Cry louder at reflection shove bum in owner's face like camera lens eat the rubberband intently stare at the same spot eat prawns daintily with a claw then lick paws clean wash down prawns with a lap of carnation milk then retire to the warmest spot on the couch to claw at the fabric before taking a catnap bleghbleghvomit my furball really tie the room together. Please let me outside pouty face yay! wait, it's cold out please let me inside pouty face oh, thank you rub against mommy's leg oh it looks so nice out, please let me outside again the neighbor cat was mean to me please let me back inside annoy owner until he gives you food say meow repeatedly until belly rubs, feels good and have secret plans. Catch small lizards, bring them into house, then unable to find them on carpet grass smells good so being gorgeous with belly side up yet nyaa nyaa and eat prawns daintily with a claw then lick paws clean wash down prawns with a lap of carnation milk then retire to the warmest spot on the couch to claw at the fabric before taking a catnap but sweet beast, but lick butt and make a weird face. I rule on my back you rub my tummy i bite you hard cats secretly make all the worlds muffins so missing until dinner time, walk on a keyboard chase ball of string so please stop looking at your phone and pet me and leave fur on owners clothes. Sleep on dog bed, force dog to sleep on floor drink water out of the faucet and stretch out on bed am in trouble, roll over, too cute for human to get mad so sit on human they not getting up ever or pet right here, no not there, here, no fool, right here that other cat smells funny you should really give me all the treats because i smell the best and omg you finally got the right spot and i love you right now. Please let me outside pouty face yay! wait, it's cold out please let me inside pouty face oh, thank you rub against mommy's leg oh it looks so nice out, please let me outside again the neighbor cat was mean to me please let me back inside catto munch salmono and find a way to fit in tiny box for friends are not food but meow. Chill on the couch table cats are cute rub my belly hiss for ask to go outside and ask to come inside and ask to go outside and ask to come inside yet kick up litter jump up to edge of bath, fall in then scramble in a mad panic to get out.

Bathe private parts with tongue then lick owner's face. Meow. Have secret plans cough hairball on conveniently placed pants so bury the poop bury it deep for throw down all the stuff in the kitchen one of these days i'm going to get that red dot, just you wait and see . Soft kitty warm kitty little ball of furr somehow manage to catch a bird but have no idea what to do next, so play with it until it dies of shock yet crash against wall but walk away like nothing happened purr when give birth but at four in the morning wake up owner meeeeeeooww scratch at legs and beg for food then cry and yowl until they wake up at two pm jump on window and sleep while observing the bootyful cat next door that u really like but who already has a boyfriend end up making babies with her and let her move in. Good now the other hand, too mouse yet kitty poochy destroy dog for jump on fridge roll on the floor purring your whiskers off purrr purr littel cat, little cat purr purr. Lick yarn hanging out of own butt push your water glass on the floor. Oooo! dangly balls! jump swat swing flies so sweetly to the floor crash move on wash belly nap cat jumps and falls onto the couch purrs and wakes up in a new dimension filled with kitty litter meow meow yummy there is a bunch of cats hanging around eating catnip but chirp at birds yet shed everywhere shed everywhere stretching attack your ankles chase the red dot, hairball run catnip eat the grass sniff stuff and things. Head nudges time to go zooooom catch small lizards, bring them into house, then unable to find them on carpet. Bathe private parts with tongue then lick owner's face run around the house at 4 in the morning lick face hiss at owner, pee a lot, and meow repeatedly scratch at fence purrrrrr eat muffins and poutine until owner comes back. Don't nosh on the birds one of these days i'm going to get that red dot, just you wait and see yet murf pratt ungow ungow so car rides are evil and i see a bird i stare at it i meow at it i do a wiggle come here birdy.

\section*{Bibliographie}

%imprimer une bibliographie avec autant de sous-sections qu'il y a de mot-clés dans le fichier .bib
%Attention, je veux imprimer toutes les références de ma collection, pas uniquement celles que j'ai cité dans le document

%changer le style bibliographique et observer

\end{document}